### 2024-08-23 Paper/paper2.tex

    I ultimately employ a synthetic difference-in-differences estimation strategy that mirrors two-way-fixed effects, where the key independent variable is the interaction between having clinically trained executives and being in years after pay-for-performance took effect. All hospitals had incentive to improve quality in response to the policy change, as penalties and payments are determined by comparing quality among hospitals. Thus, I leverage the timing of the policy change, rather than the policies themselves. One may be concerned about potential differences in quality trends between clinical and non-clinical executive team hospitals leading to a violation in the parallel trends assumption. This is why I implement a synthetic difference-in-differences estimation strategy (\cite{arkhangelsky2021synthetic}). That is, non-clinical team hospitals with trends similar to clinical team hospitals in readmission, mortality, and baseline case mix before the programs are more heavily weighted, as well as time periods that balance pre- and post-program outcomes for non-clinical teams. I present the unweighted two-way-fixed-effects specification equation for clarity, and the identification assumptions are conceptually similar for synthetic difference-in-differences.

@@

    To investigate this hypothesis empirically, I merge all general for-profit hospitals in the AHA data to the sample of nonprofit hospitals. Then, I compare readmission and mortality rates of always clinical executives and never clinical executives to for-profit hospitals after the incentive change. Ideally, I would also have leadership heterogeneity information for for-profit hospitals, but this data does not exist publicly. However, on average, for-profit hospitals have revealed through their ownership status that they more heavily weigh profit. Thus, comparing different executive team behavior to for-profit behavior helps reveal how profit driven certain leadership teams are. Thus, I estimate the weighted synthetic difference-in-differences version of

@@

\subsection{Robustness to Other Estimations}\label{app:fullsample}

In analyses presented in the main body of the paper, I use a synthetic difference-in-differences approach to identify the effect of clinically trained executives. I choose this as the main estimation strategy due to potential unobserved differences correlated with executive choice, where synthetic DiD assures parallel trends by choosing the optimal composition of control and treatment hospitals. In this section, I present results under three different estimation techniques for robustness: classic two way fixed effects, two-way fixed effects with manual weights that balance case mix index and penalties of hospitals with different leadership teams, and synthetic control.

@@

In Section \ref{sec:clinical}, I first establish the effect of clinically trained executives on response to change in incentives on quality using a synthetic difference-in-differences approach. Now, I present results using various estimation techniques in Table \ref{tab:main_twfe_match} in order to assess to robustness of this finding.

>>>>

    I ultimately employ a synthetic difference-in-differences estimation strategy that mirrors two-way-fixed effects, where the key independent variable is the interaction between having clinically trained executives and being in years after pay-for-performance took effect. All hospitals had incentive to improve quality in response to the policy change, as penalties and payments are determined by comparing quality among hospitals. Thus, I leverage the timing of the policy change, rather than the policies themselves. One may be concerned about potential differences in quality trends between clinical and non-clinical executive team hospitals leading to a violation in the parallel trends assumption. This is why I implement a synthetic difference-in-differences estimation strategy (\cite{arkhangelsky2021synthetic}). That is, non-clinical team hospitals with trends similar to clinical team hospitals in readmission, mortality, and baseline case mix before the programs are more heavily weighted, as well as time periods that balance pre- and post-program outcomes for non-clinical teams. I present the unweighted two-way-fixed-effects specification equation for clarity, and the identification assumptions are conceptually similar for synthetic difference-in-differences. In Appendix \ref{app:otherestimations}, I show that the findings are robust to using two way fixed effects, matching, or synthetic control.

@@

    The hypothesis driven from this theory is that clinically trained executives put more weight on quality of care before the financial incentives on quality began. To investigate this hypothesis empirically, I merge all general for-profit hospitals in the AHA data to the sample of nonprofit hospitals. Then, I compare readmission and mortality rates of always clinical executives and never clinical executives to for-profit hospitals after the incentive change. While I do not have information on leadership teams of for-profit hospitals, on average, they have revealed through their ownership status that they more heavily weigh profit. Thus, comparing different executive team behavior to for-profit behavior helps reveal how profit driven certain leadership teams are. Thus, I estimate the weighted synthetic difference-in-differences version of

@@

\subsection{Robustness to Other Estimations}\label{app:otherestimations}

In analyses presented in the main body of the paper, I use a synthetic difference-in-differences approach to identify the effect of clinically trained executives. I choose this as the main estimation strategy due to potential unobserved differences correlated with executive choice, where synthetic DiD assures parallel trends by choosing the optimal composition of control and treatment hospitals. As a robustness check, I now present results under three different estimation techniques for robustness: classic two way fixed effects, two-way fixed effects with manual weights that balance case mix index and penalties of hospitals with different leadership teams, and synthetic control.

For the manual weighting strategy, I apply the Coarsened Exact Matching (CEM) procedure as described by \citeauthor{azoulay2010superstar} (\citeyear{azoulay2010superstar}). This approach involves grouping hospitals based on observable characteristics such as bed size, the number of patients in each relevant condition, and eventual HRRP penalty status in each relevant condition. Hospitals are then placed into bins according to these characteristics, and matches are made exactly between hospitals within the same bin. Hospitals that do not find an exact match in this process are excluded from the sample.

@@

In Section \ref{sec:clinical}, I first establish the effect of clinically trained executives on response to change in incentives on quality using a synthetic difference-in-differences approach. Now, I present results using various estimation techniques in Table \ref{tab:main_twfe_match} in order to assess to robustness of this finding. Columns (1)-(3) present estimates and standard errors for the three estimations: TWFE, TWFE with matched sample, and synthetic control, respectively. For both TWFE and TWFE with matching, the magnitude is larger than that for synthetic DiD (0.27) and statistically significant. The estimate and standard error for synthetic control are very similar to those for synthetic DiD. In columns (4)-(6), I present the results for mortality rates, which confirm no differential response. This exercise supports the finding that clinically trained executives affect the readmission rate response of hospitals to change in incentives on quality.

### 2024-08-23 Tables/MD_noMD_readmort_decomp_synth.tex
update tables

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Exec x Post Programs & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
2012 MD Exec x Post Programs &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3005 & 1595 & 3005 & 1595\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{5}{l}{outcome variables.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\underline{Weighted Avg. Readmission Rate}} & \multicolumn{2}{c}{\underline{Weighted Avg. Mortality Rate}} \\
 & (1) & (2) & (3) & (4)\\
\midrule
Signaling Effect & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
Managing Effect &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
Observations & 3,005 & 1,595 & 3,005 & 1,595\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{5}{l}{outcome variables.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}
